Fast, Scalable Phrase-Based SMT Decoding

### 2016-06-09 acl.2016/acl2016.tex
fucking rewrite

\begin{abstract}
The utilization of statistical machine translation (SMT) has grown enormously over the last decade, many using open-source software developed by the NLP community. As commercial use has increased, there is need that for the software to be optimized for their requirements, in particular, faster phrase-based decoding and more efficient utilization of modern multicore servers.

In this paper we re-examining the major components of phrase-based decoding and decoder implementation with particular emphasis on speed and scalability on multicore machines. The result is a drop-in replacement for the Moses decoder which is up to fifteen times faster and scales monotonically with the number of cores.

@@

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400\footnote{\scriptsize the pop-limit was chosen following public discussion on finding a balance between decoding speed and translation quality with Moses for commercial use https://www.mail-archive.com/moses-support\%40mit.edu/msg13181.html }, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employed by users who require fast decoding as it gives them the ability to trade speed with translation quality via a simple pop-limit parameter.

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash 482457bf2bbb5673fbab5f663da5fd3d78ed132f } version of the Moses decoder taken from the github repository.

>>>>

\begin{abstract}
The utilization of statistical machine translation (SMT) has grown enormously over the last decade, many using open-source software developed by the NLP community. As commercial use has increased, there is need for  software that is optimized for commercial requirements, in particular, faster phrase-based decoding and more efficient utilization of modern multicore servers.

In this paper we re-examine the major components of phrase-based decoding and decoder implementation with particular emphasis on speed and scalability on multicore machines. The result is a drop-in replacement for the Moses decoder which is up to fifteen times faster and scales monotonically with the number of cores.

@@

Standard Moses phrase-based configurations are used, except that we use the cube-pruning algorithm~\cite{Chiang:2007:cl} with a pop-limit of 400\footnote{the pop-limit was chosen from public discussion on the Moses mailing list on an acceptable balance between decoding speed and translation quality with Moses for commercial use %https://www.mail-archive.com/moses-support\%40mit.edu/msg13181.html 
}, rather than the basic phrase-based algorithm. The cube-pruning algorithm is often employed by users who require fast decoding as it gives them the ability to trade speed with translation quality via a simple pop-limit parameter.

As a baseline, we use a recent\footnote{as at 8th June, 2016, commit hash \scriptsize{482457bf2bbb5673fbab5f663da5fd3d78ed132f} } version of the Moses decoder taken from the github repository.
